Comparing R packages for calculation of persistent homology

### 2020-03-19 tdabench-paper/tdabench.Rmd
fixed phrasing

Vietoris-Rips complex memory more predictable, but alpha complex memory generally better (but what about Ripser?).

@@

\section{Acknowledgments}
Emily Dolson, PhD for assistance with using a high-performance computing node for data collection.

>>>>

@@

\section{Acknowledgments}
The authors thank Emily Dolson, PhD for assistance with using a high-performance computing node for data collection.
